%% Copyright 2006-2012 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[grey]{classic}
\usepackage{hyperref}

\usepackage[utf8]{inputenc}

\firstname{Vedrana}
\familyname{Jankovi\'{c}}
\title{M.Sc. Computer Science}
\address{Mi\v{c}evec, Majur\v{c}eva 41}{10410 Velika Gorica, Croatia}
\mobile{+385 99 7878 540 }
\email{vedrana.jankovic@gmail.com}
\homepage{vedri.ca}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{August 2011}
	{European Summer School of Language, Logic and Technology}
	{} % arguments 3 to 6 can be left empty
	{}
	{}
	{}
\cventry{Sept.~2009 -- July~2011}
	{M.Sc.~in Computer Science}{University of Zagreb, Faculty of Electrical Engineering and Computing, \href{http://ktlab.fer.hr/en/home}{Knowledge Technologies Laboratory}}
	{}
	{GPA \textit{4.533} (\textit{5.00} scale)}
	{}
\cvline{Thesis title}{\emph{Computational Models of Distributional Lexical Semantics for Croatian Language}}
\cvline{Supervisors}{Assist.~Prof.~Jan \v{S}najder, Ph.D., Prof.~Bojana Dalbelo-Ba\v{s}i\'{c}, Ph.D}

\cventry{Sept.~2006 -- July~2009}
	{B.Sc.~in Computer Science}{University of Zagreb, Faculty of Electrical Engineering and Computing, \href{http://www.ccl.fer.hr}{Consumer Computing Laboratory}}
	{}
	{GPA \textit{3.697} (\textit{5.00} scale)}
	{}
\cvline{Thesis title}{\emph{Operating systems simulation gadgets}}
\cvline{Supervisor}{Prof.~Sini\v{s}a Srblji\'{c}, Ph.D}

\section{Experience}
\cventry{Sept.~2011 -- present}{Software engineer}{In2}{Croatia, Zagreb}{}{Working on implementation of platform for investment performance attribution analysis}
\cventry{July~2010 -- Sept.~2010}{Software engineer (intern)}{Ericsson Nikola Tesla}{Croatia, Zagreb}{}{Research project ``Assessment of multicore programming language'' during Summer Camp 2010}
\cventry{July 2009 -- Sept.~2009}{Software engineer (intern)}{Ericsson Nikola Tesla}{Croatia, Zagreb}{}{Research project ``PROTO: Multicore SIP parser'' during Summer Camp 2009}
\cventry{July 2008 -- Sept.~2008}{Software engineer (intern)}{Exor}{Croatia, Zagreb}{}{Worked on visualizing sets of textual algorithm schemes of semiautomated security procedures for a tunnel traffic control system.}


\section{Projects}

\cventry{2011 -- present}
	{Investment Performance Attribution Analysis}
	{\newline{}In2, Croatia, Zagreb}
	{}
	{}
	{Analyzing and implementing algorithms for portfolio performance attribution analysis, in a team of four. Implementation in Oracle DB, Java (Spring) and Adobe Flex.}

\cventry{2009 -- 2011}
	{DSM Methods for Measuring Semantic Similarity}
	{\newline{}University of Zagreb, Faculty of Electrical Engineering and Computing, Croatia}
	{}
	{\newline{}Mentors: Assist.~Prof.~Jan \v{S}najder, Ph.D., Prof.~Bojana Dalbelo-Ba\v{s}i\'{c}, Ph.D}
	{For M.Sc., worked on research and implementation of distributional semantic models (DSMs) for Croatian language. DSMs dynamically build semantic word representations in the form of multi-dimensional vector spaces through a statistical analysis of the contexts in which words occur. Geometrical relations between vectors correlate with semantic relations between represented words. Implementation in Python.}

\cventry{2011}
	{Hyperlink Constituency}
	{\newline{}Massachusetts Institute of Technology, Department of Linguistics and Philosophy}
	{\newline{}Project lead: Michael Yoshitaka Erlewine, \url{http://constituency.mit.edu}}
	{}
	{Investigating the syntactic notion of constituency by studying inline hyperlinks in a hypertext corpus. A constituent is a word or a group of words that functions as a single unit within a sentence. The project hypothesis is that inline links are constituents in their host sentences. Implementation is based on PHP and MySQL.}
 
\cventry{2011}
	{Corpus Explorer}
	{\newline{}University of Zagreb, Faculty of Electrical Engineering and Computing, Croatia}
	{}
	{\newline{}Mentor: Prof.~Bojana Dalbelo-Ba\v{s}i\'{c}, Ph.D}
	{Implemented an explorer and visualizer tool for a large corpora set of Croatian journal articles provided by Croatian News Agency, in a team of 5. Used MySQL, C\# and WPF.}

\cventry{2010}
	{Assessment of multicore programming languages}
	{\newline{}Ericsson Nikola Tesla d.d., Zagreb, Croatia}
	{}
	{\newline{}Mentor: Ivan Skuliber, Ph.D.}
	{In a team of 4 worked on evaluating multicore programming libraries for C++ (CILK), Java (JSR-166) and Erlang by implementing and testing parallel text processing, process management and message parsing. Implemented universal GLR parser in Erlang.}

\cventry{2009}
	{Using K-Nearest Neighbor Method for Playing Cards Recognition }
	{\newline{}University of Zagreb, Faculty of Electrical Engineering and Computing, Croatia}
	{}{}
	{In a team of 4, as part of the Machine Learning course, implemented an image detection and recognition system used for recognizing playing cards. Implementation based on C\#.}

\cventry{2009}
	{Neural Network Character Recognition}
	{\newline{}University of Zagreb, Faculty of Electrical Engineering and Computing, Croatia}
	{}{}
	{Worked in a team of 6 on modeling and implementing handwritten characters recognition system using multilayer neural network as part of the Pattern Recognition Learning course. The implementation was based on C\# and OpenCV.}

\cventry{2009}
	{PROTO: Multicore SIP parser}
	{\newline{}Ericsson Nikola Tesla d.d., Zagreb, Croatia}
	{}
	{\newline{}Mentor: Ivan Skuliber, Ph.D.}
	{Worked in a team of 4 on the design and implementation of a 100\% compliant SIP parser for use in multicore processor systems. Implementation was based on C\# and XML. }

\section{Technical Skills}
\cvline{Programming languages}{strong in Java (SE, EE) and Python, experience with Flex, C\#, Erlang, PHP, JavaScript}
\cvline{Other technologies}{LaTex, SQL, PL/SQL}

\section{Academic Publications}
\cvline{5 Sept.~2011}{\textbf{Random Indexing Distributional Semantic Models for Croatian Language}, \hspace{4ex} \textit{Vedrana Jankovi\'{c}, Jan \v{S}najder, Bojana Dalbelo-Ba\v{s}i\'{c}}, Balto-Slavonic Natural Language Processing 2011}
\cvline{15 Sept.~2011}{\textbf{Multicore SIP Parsing with Imperative and Declarative Implementations}, \textit{Ivan Skuliber, Vedrana Jankovi\'{c}, Ru\v{z}ica Zec}, International Conference on Software, Telecommunications and Computer Networks 2011}

\section{Awards}
\cvline{2010}{Applicability of Multicore Programming Libraries in Parsing  awarded as Student project of the year, 1st prize, Ericsson NT, Croatia, Zagreb}
\cvline{2009}{Multicore SIP  awarded as Student project of the year, 1st prize, Ericsson NT, Croatia, Zagreb}
\cvline{2006}{Croatian State Mathematics Championship 2nd place on final round, state level}
\cvline{2006, 2005, 2004}{Croatian State Championship in Croatian Language Grammar and Orthography final rounds, state level}

\section{Languages}
\cvline{Croatian}{mother tongue}
\cvline{English}{writing and speaking proficiency, 17 years of studying and active usage, CAE diploma}
\cvline{French}{good writing and speaking skills, 9 years of studying and usage, DELF B2 diploma}

\section{Interests}
\cvline{Music}{DJ-ed at KSET student club (\url{http://www.kset.org/}), 2007 -- 2009}
\cvline{Journalism}{student journalist for Panoptikum, student newspaper, University of Zagreb, 2008; proofreading for Pro Tempore, student journal, Faculty of Humanities and Social Sciences, 2010, 2011}
\cvline{Literature}{I really love reading}
\cvline{Other}{student representative at the Faculty Council, Faculty of Electrical Engineering and Computing, 2008 -- 2010}

\end{document}

